%!TEX TS-program = xelatex
\documentclass[10pt]{friggeri-cv}

\begin{document}
\header{Eric}{Moynihan}
       {Full Stack Developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Cork,
    Ireland
    ~
    \href{mailto:eric@moynihan.io}{eric@moynihan.io}
    \href{http://moynihan.io}{http://moynihan.io}
    \href{http://github.com/ericm}{github.com/ericm}
    \href{https://www.linkedin.com/in/eric-moynihan}{linkedin.com/in/eric-moynihan}
  \section{languages}
    english/irish
  \section{technologies}
    Python, Go, Kotlin,
    Java, Rust, PHP,
    Git, GitHub,
    Linux, Bash, Docker
    ~
    {\color{red} $\varheartsuit$} JavaScript/TypeScript
    (ES6, node.js, React JSX, TSX, Angular, Express, Parcel, Electron, Webpack, NPM, etc.)
    CSS3 \& HTML5
    
\end{aside}

\section{applications}

Here are some projects I've done:

\begin{entrylist}
  \entry
    {2019}
    {Yup}
    {\href{https://github.com/ericm/yup}{github.com/ericm/yup}}
    {Arch Linux AUR Helper with ncurses functionality and better searching and sorting. Made in Go. }
  \entry
    {2018}
    {Newlogic}
    {\href{https://github.com/ericm/newlogic}{github.com/ericm/newlogic}}
    {A Circuit Builder / Logic Design Desktop Application (like mmlogic) made with Electron + React Typescript. It's currently compatible with Windows, Mac and Linux. Made with TypeScript/Electron}
  \entry
    {2018}
    {Py The Way}
    {\href{https://github.com/py-the-way/py-the-way}{github.com/py-the-way/py-the-way}}
    {This project is a recommendation system that recommends where a user should live in the US using big data, python and pandas. It was originally made for an IBM sponsored \textbf{hackathon where it came first place.}. Made with Python and Pandas}
  \entry
    {2018}
    {RSS Feed Reader Plus}
    {\href{https://github.com/ericm/RSS-Feed-Reader-Plus}{github.com/ericm/RSS-Feed-Reader-Plus}}
    {Advanced Multi-Platform Desktop RSS Feed Reader with support for: Rules and Cloud Sync. Made with JavaScript and Electron}
  \entry
    {2017}
    {metar-pro}
    {\href{https://github.com/ericm/metar-pro}{github.com/ericm/metar-pro}}
    {Web App designed to predict what runway a plane will land on using current data. The landing direction is then illustrated using Google Maps Api.}
  \entry
    {2015}
    {West Muskerry AC Website}
    {Website}
    {A website and custom CMS written in PHP for a local sports club}

\end{entrylist}

\section{activities and volunteering}
\begin{itemize}
    \item UCC Netsoc. Attended tech talks and meetups.
    \item CoderDojo. \textbf{Mentor of the Advanced Web Dev} in The IBM Cork CoderDojo.
    \item Class Representative of CK401 2022 for the year 2019/2020.
    \item Qualified as a pool \textbf{lifeguard} from the \textit{Royal Life Saving Society}.
\end{itemize}

\section{education}

\begin{entrylist}
  \entry
    {since 2018}
    {Computer Science in {\normalfont University College Cork}}
    {Cork, Ireland}
    {\emph{Achieved first class honours in every module so far}}
  \entry
    {2012-2018}
    {De La Salle College}
    {Macroom, Co. Cork}
    {Secondary School, Achieving high results in 7 Higher Level subjects}
  \entry
    {2004-2012}
    {Canovee NS}
    {Carrigadrohid, Macroom, Co. Cork}
    {Primary School}
\end{entrylist}
\newline\newline\newline
\section{experience}

\begin{entrylist}
  \entry
    {2019-present}
    {Lab Demonstrator - {\normalfont University College Cork}}
    {Student Part-Time Job}
    {\emph{Demonstrating for first year students in the \textit{Introduction to Programming} lab}}
  \entry
    {2019-present}
    {IT Services - {\normalfont University College Cork}}
    {Student Part-Time Job}
    {\emph{Working in the Staff IT frontdesk assisting all UCC staff members in with IT related queries.}}
  \entry
    {2019}
    {Rock Bingo}
    {Summer job}
    {\emph{Called numbers for linked games (cross-country) and general staff duties}}
  \entry
    {2016-present}
    {Southern Star}
    {Newspaper job}
    {\emph{Writing weekly local news roundup}}
  \entry
    {2014}
    {IBM Cork}
    {Transition year work experience}
    {\emph{Ran tests on bluemix twitter API.}}
\end{entrylist}




\end{document}
